Summary Tables

### 2020-03-19 summary_tables_outcomes.Rmd
Comment out YLLs

### Change in YLL {#change_YLL}

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)])
    sapply(sort(unique(xx$age_cat)),function(z)
      sum(xxx[xx$age_cat==z]))
  })
  colnames(temp) <- scen_names
  temp
})
sum_and_round_and_print(yll_totals,"Change in YLL total in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs per 100,000 {#change_YLL_age_100k}

```{r scen_prop = "asis"}
yll_rates <- lapply(cities,function(x) rbind(yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

YLLs per 100,000 people by gender by age group scenario

### Change in YLLs per 100,000 {#change_YLL_gender_age_100k}

```{r scen_prop = "asis"}
yll_totals <- lapply(io,function(x){
  temp <- sapply(1:5,function(y){
    xx <- x$outcomes$hb$ylls
    rowSums(xx[,seq(2+y,ncol(xx),by=5)])
  })
  rownames(temp) <- apply(x$outcomes$hb$deaths[,1:2],1,function(z)paste0(z[1],'_',z[2]))
  colnames(temp) <- scen_names
  temp
})

yll_rates <- lapply(cities,function(x) 
  rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/
          t(repmat(io[[x]]$demographic$population,5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(yll_rates) <- cities
round_and_print(yll_rates,"Change in YLLs per 100,000 in ")
```

@@

### Change in YLLs due to injury {#change_yll_injury}

```{r}
injury_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y])))
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(injury_totals,"Change in YLLs due to injury in ")
```

### Change in YLLs due to PA {#change_yll_PA}
```{r}
pa_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ")
```

### Change in YLLs due to AP {#change_yll_AP}
```{r}
ap_totals <- lapply(io,function(x){
  xx <- x$outcomes$pathway_hb$ylls
  xxx <- sapply(1:5,function(y){
    xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]])
    sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z]))
  })
  colnames(xxx) <- scen_names
  xxx
})
sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ")
```

YLLs per 100,000 people by age group by scenario

### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k}

```{r scen_prop = "asis"}
injury_rates <- lapply(cities,function(x) rbind(injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(injury_rates) <- cities
round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ")
```

### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k}
```{r}
pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(pa_rates) <- cities
round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ")
```

### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k}
```{r}
ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(ap_rates) <- cities
round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ")
```

## BY DISEASE

Change in deaths total (for the city based on real population size) by scenario

### Change in deaths due to disease {#change_death_disease}

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$deaths
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ")

Change in deaths per 100,000 people by scenario

### Change in deaths due to disease per 100,000 {#change_death_disease_100k}

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ")
```

Change in YLL total (for the city based on real population size) by scenario

### Change in YLL due to disease {#change_yll_disease}

disease_totals <- lapply(io,function(x){
  xx <- x$outcomes$hb$ylls
  xxx <- sapply(1:5,function(y){
    colSums(xx[,seq(y+2,ncol(xx),by=5)])
  })
  colnames(xxx) <- scen_names
  rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y))
  xxx
})
sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ")

### Change in YLL due to disease per 100,000 {#change_yll_disease_100k}

```{r scen_prop = "asis"}
disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000))
names(disease_rates) <- cities
round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ")
```

>>>>

<!-- ### Change in YLL {#change_YLL} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- yll_totals <- lapply(io,function(x){ -->
<!--   temp <- sapply(1:5,function(y){ -->
<!--     xx <- x$outcomes$hb$ylls -->
<!--     xxx <- rowSums(xx[,seq(2+y,ncol(xx),by=5)]) -->
<!--     sapply(sort(unique(xx$age_cat)),function(z) -->
<!--       sum(xxx[xx$age_cat==z])) -->
<!--   }) -->
<!--   colnames(temp) <- scen_names -->
<!--   temp -->
<!-- }) -->
<!-- sum_and_round_and_print(yll_totals,"Change in YLL total in ") -->
<!-- ``` -->

<!-- YLLs per 100,000 people by age group by scenario -->

<!-- ### Change in YLLs per 100,000 {#change_YLL_age_100k} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- yll_rates <- lapply(cities,function(x) rbind(yll_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(yll_rates) <- cities -->
<!-- round_and_print(yll_rates,"Change in YLLs per 100,000 in ") -->
<!-- ``` -->

<!-- YLLs per 100,000 people by gender by age group scenario -->

<!-- ### Change in YLLs per 100,000 {#change_YLL_gender_age_100k} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- yll_totals <- lapply(io,function(x){ -->
<!--   temp <- sapply(1:5,function(y){ -->
<!--     xx <- x$outcomes$hb$ylls -->
<!--     rowSums(xx[,seq(2+y,ncol(xx),by=5)]) -->
<!--   }) -->
<!--   rownames(temp) <- apply(x$outcomes$hb$deaths[,1:2],1,function(z)paste0(z[1],'_',z[2])) -->
<!--   colnames(temp) <- scen_names -->
<!--   temp -->
<!-- }) -->

<!-- yll_rates <- lapply(cities,function(x)  -->
<!--   rbind(yll_totals[[x]][match(apply(io[[x]]$demographic[,c('sex','age')],1,function(z)paste0(z[2],'_',z[1])),rownames(yll_totals[[x]])),]/ -->
<!--           t(repmat(io[[x]]$demographic$population,5,1))*100000, Total=colSums(yll_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(yll_rates) <- cities -->
<!-- round_and_print(yll_rates,"Change in YLLs per 100,000 in ") -->
<!-- ```  -->

@@

<!-- ### Change in YLLs due to injury {#change_yll_injury} -->

<!-- ```{r} -->
<!-- injury_totals <- lapply(io,function(x){ -->
<!--   xx <- x$outcomes$hb$ylls -->
<!--   xxx <- sapply(1:5,function(y)sapply(sort(unique(xx$age_cat)),function(z)sum(xx[xx$age_cat==z,injury_col-1+y]))) -->
<!--   colnames(xxx) <- scen_names -->
<!--   xxx -->
<!-- }) -->
<!-- sum_and_round_and_print(injury_totals,"Change in YLLs due to injury in ") -->
<!-- ``` -->

<!-- ### Change in YLLs due to PA {#change_yll_PA} -->
<!-- ```{r} -->
<!-- pa_totals <- lapply(io,function(x){ -->
<!--   xx <- x$outcomes$pathway_hb$ylls -->
<!--   xxx <- sapply(1:5,function(y){ -->
<!--     xxx <- rowSums(xx[,pa_cols[seq(y,length(pa_cols),by=5)]]) -->
<!--     sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z])) -->
<!--   }) -->
<!--   colnames(xxx) <- scen_names -->
<!--   xxx -->
<!-- }) -->
<!-- sum_and_round_and_print(pa_totals,"Change in YLLs due to PA in ") -->
<!-- ``` -->

<!-- ### Change in YLLs due to AP {#change_yll_AP} -->
<!-- ```{r} -->
<!-- ap_totals <- lapply(io,function(x){ -->
<!--   xx <- x$outcomes$pathway_hb$ylls -->
<!--   xxx <- sapply(1:5,function(y){ -->
<!--     xxx <- rowSums(xx[,ap_cols[seq(y,length(ap_cols),by=5)]]) -->
<!--     sapply(sort(unique(xx$age_cat)),function(z)sum(xxx[xx$age_cat==z])) -->
<!--   }) -->
<!--   colnames(xxx) <- scen_names -->
<!--   xxx -->
<!-- }) -->
<!-- sum_and_round_and_print(ap_totals,"Change in YLLs due to AP in ") -->
<!-- ``` -->

<!-- YLLs per 100,000 people by age group by scenario -->

<!-- ### Change in YLLs due to injury per 100,000 {#change_yll_injury_100k} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- injury_rates <- lapply(cities,function(x) rbind(injury_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(injury_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(injury_rates) <- cities -->
<!-- round_and_print(injury_rates,"Change in YLLs due to injury per 100,000 in ") -->
<!-- ``` -->

<!-- ### Change in YLLs due to PA per 100,000 {#change_yll_PA_100k} -->
<!-- ```{r} -->
<!-- pa_rates <- lapply(cities,function(x) rbind(pa_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(pa_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(pa_rates) <- cities -->
<!-- round_and_print(pa_rates,"Change in YLLs due to PA per 100,000 in ") -->
<!-- ``` -->

<!-- ### Change in YLLs due to injury AP 100,000 {#change_yll_AP_100k} -->
<!-- ```{r} -->
<!-- ap_rates <- lapply(cities,function(x) rbind(ap_totals[[x]]/t(repmat(pop_by_age[[x]],5,1))*100000, Total=colSums(ap_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(ap_rates) <- cities -->
<!-- round_and_print(ap_rates,"Change in YLLs due to AP per 100,000 in ") -->
<!-- ``` -->

<!-- ## BY DISEASE -->

<!-- Change in deaths total (for the city based on real population size) by scenario -->

<!-- ### Change in deaths due to disease {#change_death_disease} -->

<!-- ```{r} -->

<!-- disease_totals <- lapply(io,function(x){ -->
<!--   xx <- x$outcomes$hb$deaths -->
<!--   xxx <- sapply(1:5,function(y){ -->
<!--     colSums(xx[,seq(y+2,ncol(xx),by=5)]) -->
<!--   }) -->
<!--   colnames(xxx) <- scen_names -->
<!--   rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y)) -->
<!--   xxx -->
<!-- }) -->
<!-- sum_and_round_and_print(disease_totals,"Change in deaths due to disease in ") -->

<!-- ``` -->

<!-- Change in deaths per 100,000 people by scenario -->

<!-- ### Change in deaths due to disease per 100,000 {#change_death_disease_100k} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(disease_rates) <- cities -->
<!-- round_and_print(disease_rates,"Change in deaths due to disease per 100,000 in ") -->
<!-- ``` -->

<!-- Change in YLL total (for the city based on real population size) by scenario -->

<!-- ### Change in YLL due to disease {#change_yll_disease} -->

<!-- ```{r} -->

<!-- disease_totals <- lapply(io,function(x){ -->
<!--   xx <- x$outcomes$hb$ylls -->
<!--   xxx <- sapply(1:5,function(y){ -->
<!--     colSums(xx[,seq(y+2,ncol(xx),by=5)]) -->
<!--   }) -->
<!--   colnames(xxx) <- scen_names -->
<!--   rownames(xxx) <- sapply(rownames(xxx),function(y)gsub('scen1_','',y)) -->
<!--   xxx -->
<!-- }) -->
<!-- sum_and_round_and_print(disease_totals,"Change in YLL due to disease in ") -->

<!-- ``` -->

<!-- ### Change in YLL due to disease per 100,000 {#change_yll_disease_100k} -->

<!-- ```{r scen_prop = "asis"} -->
<!-- disease_rates <- lapply(cities,function(x) rbind(disease_totals[[x]]/sum(pop_by_age[[x]])*100000, Total=colSums(disease_totals[[x]])/rep(sum(pop_by_age[[x]]),length=5)*100000)) -->
<!-- names(disease_rates) <- cities -->
<!-- round_and_print(disease_rates,"Change in YLL due to disease per 100,000 in ") -->
<!-- ``` -->
